\chapter*{Conclusion}
The present report is the result of the experience and know-how acquired during our four-month internship at the Orange Digital Center. 
This internship has been very instructive in terms of the knowledge we have gained both technically and professionally. 
Indeed, throughout this internship,
 we have been able to put into practice the theoretical knowledge we studied over our three years of a bachelor's degree in information technology at the ISET of Kairouan,

  adjust and enrich them to meet the needs of our internship.

As part of our final year project, we proposed to develop a web application that automates the recruitment process and evaluation tests within ODC.
 This platform allows for the evaluation of candidates who apply through the Orange Innovation platform. This work has also provided us with significant benefits on several levels.

Technically, we learned to handle the REACT library, services developed by NodeJS, 
and many other tools. We also had the opportunity to master design using UML and graphic design with XD. 
The daily internship at the company was also a unique opportunity for us,
 providing significant enrichment on a relational level.

Although the main objectives of our project have been achieved, the system we developed is intended to be enhanced with additional advanced features and improvements, such as adding a module that allows a candidate to answer questions with pieces of code that will be executed online. The operating principle would be similar to sites like Coding Game or Hacker Rank.

Furthermore, the recruitment team will have more information about the candidate. Indeed, the requirement to code to answer a question mobilizes more skills than a simple knowledge questionnaire.